High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-05 notebooks/mnist.qmd
pfff

```{julia}
epochs = 100
clf = NeuralNetworkClassifier(
    builder=MLJFlux.MLP(hidden=(32,), σ=relu), 
    epochs=epochs,
    batch_size=Int(round(n_obs/10))
)
conf_model = conformal_model(clf; method=:simple_inductive)
mach = machine(conf_model, X, labels)
fit!(mach)
```

@@

```{julia}
using CounterfactualExplanations.DataPreprocessing: undersample
dt_reduced = undersample(counterfactual_data, 100)
# dt_reduced = counterfactual_data
```

>>>>

```{julia}
epochs = 100
clf = NeuralNetworkClassifier(
    builder=MLJFlux.MLP(hidden=(32,), σ=relu), 
    epochs=epochs,
    batch_size=Int(round(n_obs/10))
)
conf_model = conformal_model(clf; method=:simple_inductive, coverage=.99)
mach = machine(conf_model, X, labels)
fit!(mach)
```

@@

```{julia}
using CounterfactualExplanations.DataPreprocessing: undersample
dt_reduced = undersample(counterfactual_data, 100)
dt_reduced = counterfactual_data
```
